\bfseries\LARGE\singlespacing{Spatiotemporal risks of \emph{Mycobacterium tuberculosis} transmission: A modelling study of environmental, clinical, and patient movement data}

### 2024-03-04 doc/paper/manuscript.tex
Updates from Overleaf

>>>>

Over the five study days, 894 patients have been registered in the clinical database, of which seven patients were diagnosed with TB and 28 patients were suspected of TB following symptom screening (\supp~Figure~\zref{fig:clinical-data}). Overall, 1,701 unique patient movements were identified after processing the video sensor data. Most patient movements were detected in the waiting room (\Cref{fig:input-data-descriptives}a) and during the morning (\Cref{fig:input-data-descriptives}b). Clinical attendees spent spend around half an hour in the clinic (median 24 minutes, interquartile range [IQR] 12$-$45), and several attendees spent more than an hour in the clinic, most of it in the waiting room (\Cref{fig:input-data-descriptives}c). During their visit, close contacts, defined as an interaction with another attendee within 1m for more than 1min, were frequent (median 5, IQR 2$-$9), and several attendees had more than 10 close contacts (\Cref{fig:input-data-descriptives}d). The majority of clinical attendees was in close contact with at least one other attendee for more than half the time of their visit (median 68\%, IQR 41\%$-$87\%, \Cref{fig:input-data-descriptives}e). The CO$_2$ levels inside the clinic were low, peaking at only about 600\,ppm in the morning (\Cref{fig:input-data-descriptives}f). Based on room size, time-varying occupancy, and CO$_2$ levels, the estimated air change rates indicated that the clinic was well-ventilated, especially the waiting room (median 29 air changes per hour, IQR 9$-$36) and corridor (median 28, IQR 16$-$36), with lower rates in the less frequently occupied TB room (median 6, IQR 5$-$12, \Cref{fig:input-data-descriptives}g).
